Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-15 paper.tex
Added comment and figures for figures for user/item factors

 \note{Soudabeh, add figure with two 3D plots showing the 3 factors of 
 every item and subject. Comment: the method indeed separates files in 
 3 blocks (for 8 types) and subjects in 8 types.}

>>>>

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
\caption{The three subject latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:userfactors}
\end{figure}

As in figures ~\ref{fig:userfactors} and  ~\ref{fig:itemfactors} shown by use of three latent factors the RFNU method indeed separates the files of synthetic matrix of 8 subject type into three blocks and also its subjects into eight types.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
\caption{The three file latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:itemfactors}
\end{figure}
